Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-26 Papers/ms.tex
long caption

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens.pdf}
\caption{The marginal posterior distribution for $N_{\rm lens}$, the
number of substructures in the lens.\label{fig:N_lens}}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{N_lens.pdf}
\caption{The marginal posterior distribution for $N_{\rm lens}$, the
number of substructures in the lens. The prior was uniform and the true
value used to generate the data was 1. However, the data is only informative
enough to suppress the probability of values above 1 slightly, since it
is possible (given this data) that low mass substructures might exist somewhere,
or that what we think is one substructure might actually be two close together,
and other such possibilities.
\label{fig:N_lens}}
\end{center}
\end{figure}
